Model for Porous Silicon Structures with a Lateral Gradient

### 2020-11-10 paper.tex
Modify Cristian's name
colocambo la subsecion del sem

\title{Model for Porous Silicon Structures with a Lateral Gradient}
\author[1]{C. A. Ospina de la Cruz}
\author[2,3]{V. Agarwal}
\author[3]{W. L. Mochán}

@@

\subsection{Scanning Electron Microscopy}
\notaL{Insert a paragraph explaining something about how the
  micrographs were obtained. Choose an appropriate title for the
  subsection. Include the definition of the acronym SEM}

@@

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. VA acknowledges support from CONACyT Basic Sciences project
A-S1 30393 and from PRODEP, and is grateful to ICF where she spent a
sabatical. CODLC is grateful for a scholarship from CONACyT.
\bibliographystyle{unsrt}
\bibliography{bibligrin}
\end{document}

>>>>

\title{Model for Porous Silicon Structures with a Lateral Gradient}
\author[1]{C. A. Ospina-Delacruz}
\author[2,3]{V. Agarwal}
\author[3]{W. L. Mochán}

@@

\notaC{\subsection{Morphological studies}}
\notaC{The morphologies of the etched porous layers (plan-view and cross-sectional) was observed using 
(SEM) scanning electron microscopy (Hitachi SU1510  High Technologies Canada, 
Inc., Toronto, Canada), the thickness  and porosity  of each fabricated  film was measured.}
\notaL{Insert a paragraph explaining something about how the
  micrographs were obtained. Choose an appropriate title for the
  subsection. Include the definition of the acronym SEM}

@@

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. VA acknowledges support from CONACyT Basic Sciences project
A-S1 30393 and from PRODEP, and is grateful to ICF where she spent a
sabatical. CAOD is grateful for a scholarship from CONACyT.
\bibliographystyle{unsrt}
\bibliography{bibligrin}
\end{document}
